A 2-Norm Condition Number for B\'{e}zier Curve Intersection

### 2019-06-17 doc/paper.tex
Removing extra "and" from Theorem 4.1.

\begin{theorem}\label{thm:kappa-closed-form}
Let \(\left[\begin{array}{c} \alpha \\ \beta \end{array}\right]\) be a
transversal intersection of two planar B\'{e}zier curves \(b_0(s)\) and
\(b_1(t)\). Then the root condition number of the intersection is
\begin{equation}\label{eq:kappa-max}
\kappa_{\alpha, \beta} = \sqrt{\frac{\mu_1^2
  \left(\bm{v} \cdot \bm{v}\right) +
  2 \mu_1 \mu_2 \left|\bm{v} \cdot \bm{w}\right| +
  \mu_2^2 \left(\bm{w} \cdot \bm{w}\right)}{\alpha^2 + \beta^2}}
\end{equation}
where
\begin{equation}
  J^{-1}\left(\alpha, \beta\right) = \left[ \begin{array}{c c}
  \bm{v} & \bm{w} \end{array}\right] \qquad
  \mu_1 = \widetilde{x}_0(\alpha) + \widetilde{x}_1(\beta) \qquad
  \mu_2 = \widetilde{y}_0(\alpha) + \widetilde{y}_1(\beta).
\end{equation}
Here \(b_0(s) = \left[\begin{array}{c c} x_0(s) & y_0(s)\end{array}\right]^T\)
and \(b_1(t) = \left[\begin{array}{c c} x_1(t) & y_1(t)\end{array}\right]^T\)
and the \(\widetilde{x}_i, \widetilde{y}_j\) are as defined in
\eqref{eq:p-tilde}.
\end{theorem}

>>>>

\begin{theorem}\label{thm:kappa-closed-form}
Let \(\left[\begin{array}{c} \alpha \\ \beta \end{array}\right]\) be a
transversal intersection of two planar B\'{e}zier curves \(b_0(s)\) and
\(b_1(t)\). Then the root condition number of the intersection is
\begin{equation}\label{eq:kappa-max}
\kappa_{\alpha, \beta} = \sqrt{\frac{\mu_1^2
  \left(\bm{v} \cdot \bm{v}\right) +
  2 \mu_1 \mu_2 \left|\bm{v} \cdot \bm{w}\right| +
  \mu_2^2 \left(\bm{w} \cdot \bm{w}\right)}{\alpha^2 + \beta^2}}
\end{equation}
where
\begin{equation}
  J^{-1}\left(\alpha, \beta\right) = \left[ \begin{array}{c c}
  \bm{v} & \bm{w} \end{array}\right] \qquad
  \mu_1 = \widetilde{x}_0(\alpha) + \widetilde{x}_1(\beta) \qquad
  \mu_2 = \widetilde{y}_0(\alpha) + \widetilde{y}_1(\beta).
\end{equation}
Here \(b_0(s) = \left[\begin{array}{c c} x_0(s) & y_0(s)\end{array}\right]^T\),
\(b_1(t) = \left[\begin{array}{c c} x_1(t) & y_1(t)\end{array}\right]^T\)
and the \(\widetilde{x}_i, \widetilde{y}_j\) are as defined in
\eqref{eq:p-tilde}.
\end{theorem}
